Generating the Blueprints of the Java Ecosystem

### 2015-03-30 msr2015-camera-ready.tex
final touch

@@

This research has been co-financed by the European Union (European So- cial Fund esf) and Greek national funds through the Operational Program ``Education and Lifelong Learning'' of the National Strategic Reference Frame- work (nsrf) - Research Funding Program: Thalis Athens University of Economics and Business - software engineering research platform.

>>>>

\clubpenalty = 10000
\widowpenalty = 10000
\displaywidowpenalty = 10000

\usepackage{flushend}

@@

This research has been co-financed by the European Union (European Social Fund esf) and Greek national funds through the Operational Program ``Education and Lifelong Learning'' of the National Strategic Reference Framework (nsrf) - Research Funding Program: Thalis Athens University of Economics and Business - software engineering research platform.
